%!TEX root = ../main.tex
\section*{Introduction}

Enterprise document and records management systems (DMS/RMS) are fundamental components of contemporary information infrastructures. 
They ensure structured storage, controlled access, traceability, and lifecycle management of organizational documents. 
In regulated environments, such systems must additionally support compliance with legal and normative requirements related to classification schemes, retention periods, disposal procedures, and auditability.

While traditional document management platforms primarily address storage and retrieval functionality, advanced process coordination is often delegated to separate workflow or business process management systems. 
This architectural separation increases integration complexity, introduces data redundancy, and may result in inconsistencies in document lifecycle control. 
Consequently, organizations face challenges in maintaining a coherent link between records management principles and operational process execution. 
Existing standards such as ISO 15489 and MoReq2010 define conceptual and functional requirements for records management~\cite{iso15489,moreq2010}, yet their practical integration with configurable workflow engines is frequently left to system-specific implementations.

This paper presents the design and implementation of a prototype enterprise document and records management system with integrated workflow support. 
The proposed solution adopts a unified architectural approach in which structured records modeling and configurable workflow execution are treated as mutually dependent components rather than isolated subsystems. 
The system is implemented using modern architectural principles, emphasizing modularity, scalability, and compliance-oriented data modeling.

The primary contribution of this work lies in: 
(i) the integration of a versioned and configurable workflow engine directly into a structured records management model, 
(ii) the alignment of workflow execution mechanisms with hierarchical classification structures and retention policies, and 
(iii) the architectural design of a modular system that supports auditability and extensibility without sacrificing maintainability.

The objective of this paper is to describe the architectural design, data model, workflow engine structure, and compliance mechanisms of the proposed solution, 
and to demonstrate how these elements form a coherent and extensible enterprise-ready system.