%!TEX root = ../main.tex
\section{Background and Related Work}

Document and records management systems have long been examined within the field of enterprise information systems and information governance. 
Normative frameworks such as ISO 15489 and MoReq2010 define conceptual and functional requirements for records lifecycle management, including classification schemes, retention schedules, disposal procedures, and auditability~\cite{iso15489,moreq2010}. 
These standards emphasize structured metadata models, hierarchical classification, and controlled disposition mechanisms to ensure long-term traceability and legal compliance.

From an architectural perspective, contemporary enterprise software increasingly adopts service-oriented or microservice-based approaches to enhance scalability, modularity, and independent component evolution. 
At the same time, workflow management systems and business process engines have evolved to support configurable process definitions, dynamic routing logic, and distributed task orchestration. 
Such systems frequently rely on graph-based process representations and versioned execution models to enable adaptability in changing business environments.

Despite these advancements, document management and workflow orchestration are commonly implemented as separate subsystems. 
In many enterprise solutions, workflow engines operate on top of document repositories through integration layers or API-based coupling. 
While this separation promotes loose coupling, it can also introduce inconsistencies in lifecycle state management, duplication of contextual data, and increased architectural complexity. 
The document lifecycle may be governed partly by records management rules and partly by external workflow states, leading to potential ambiguity in compliance-sensitive scenarios.

Several research contributions and industrial platforms propose tighter integration between content management and process execution. 
However, existing implementations often prioritize either robust document storage with compliance support or highly flexible workflow orchestration, rather than designing both aspects as inherently interdependent components of a single domain model.

The approach presented in this paper builds upon established records management principles while embedding a configurable workflow engine directly into the core data and execution model of the system. 
Instead of treating workflow as an external automation layer, workflow execution is aligned with classification structures, retention logic, and audit mechanisms. 
The contribution does not redefine existing standards, but demonstrates an architectural strategy for integrating compliance-oriented records modeling with versioned and extensible workflow execution within a unified enterprise system.
