%!TEX root = ../main.tex
\section{Discussion}

The presented architecture demonstrates that integrating records management and workflow orchestration within a unified domain model can reduce structural fragmentation commonly observed in enterprise information systems. 
In traditional environments, document storage, lifecycle management, and process execution are frequently implemented as loosely coupled subsystems connected through integration layers. 
Such separation often introduces synchronization challenges, redundant state representations, and increased operational complexity.

By embedding workflow execution directly into the records management model, the proposed system maintains a single source of truth for both document state and process state. 
This architectural consolidation reduces impedance mismatch between storage and orchestration layers and enables consistent lifecycle tracking across document-related activities.

The separation between workflow definitions (design-time structures) and workflow instances (runtime state) represents a deliberate design decision aimed at balancing configurability and stability. 
Versioned definitions allow process evolution without disrupting historical executions, supporting auditability and reproducibility. 
This distinction is particularly relevant in compliance-sensitive environments, where historical process logic must remain reconstructible.

From a scalability perspective, the service-oriented backend architecture allows modular evolution of individual components and supports horizontal scaling of stateless services. 
The introduction of asynchronous messaging for workflow-related events decouples long-running operations from synchronous API interactions, improving system responsiveness and fault tolerance. 
This event-driven model aligns with contemporary distributed system design practices and enhances resilience under variable load conditions.

The hybrid metadata persistence strategy—combining relational schema definitions with serialized runtime payloads—provides flexibility while preserving structural validation guarantees. 
However, this approach also introduces trade-offs. 
Serialized metadata values may limit direct relational querying capabilities and can require additional processing for analytical scenarios. 
Future extensions may consider selective indexing or projection strategies for frequently queried metadata attributes.

Despite these strengths, certain limitations remain. 
While the system structurally supports retention policies and disposal types, automated lifecycle enforcement and large-scale disposal workflows require further empirical validation. 
In addition, comprehensive performance benchmarking under high concurrency and distributed deployment scenarios would provide deeper insight into system behavior at scale.

Overall, the architectural design establishes a technically coherent foundation for enterprise-grade document and records management systems. 
The integration of classification hierarchies, configurable metadata, workflow orchestration, and compliance-oriented modeling demonstrates that flexibility and regulatory alignment need not be treated as mutually exclusive design goals.
